---
title: "Paper2 DHS Diet Diversity - Global regression at cluster level"
author: "Piyush Mehta"
last updated: Feb2,25
output: html_document

# This code is for All_data_v6.dta that has all countries
# Fixed effects model

# Running regressions with the AEI variable that contains the AEI of the year closest to the DHS survey year for each cluster
# Running regressions for 3 models (overall, sust and unsust) and plotting them together for the manuscript figure

#May3,24 (version11 manuscript) - not keeping the AEI change variable
---

# PLOT MODELS TOGETHER
```{r results='hide', message=FALSE, warning=FALSE}
library(dotwhisker)
library(dplyr)
library('lme4')
library('lmerTest')
library('MuMIn')
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(ggplot2)
library(expss)
library(car)
library(broom.mixed)
library(ggplot2)
library(forcats)
library(extrafont)
library(ggplot2)
library(ggrepel)
library(viridis)
#library(tidyverse)
# need to import fonts so that TW Cen font can work
#font_import()
#loadfonts(device = "win")

setwd("D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\")

```
# Load all data
```{r}

df = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Global.csv')
df_sust = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Global_sust.csv')
df_unsust = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Global_unsust.csv')

```



# All models
```{r results='hide', message=FALSE, warning=FALSE}

# (Model 1) Overall
model1 = lm(diet_m ~ aei_closest_std  + treecov_std + disturban_cat_std + distroad_cat_std + popden_std + tlu_std + age_std + education_std + improvedtoilet + improvedwater + sex + timewater_std + wealthindex_std + factor(yeardhs) + factor(country) , df)

# (Model 2) Sustainable
model2 = lm(diet_m ~ aei_closest_std  + treecov_std + disturban_cat_std + distroad_cat_std + popden_std + tlu_std + age_std + education_std + improvedtoilet + improvedwater + sex + timewater_std + wealthindex_std + factor(yeardhs) + factor(country), df_sust)

# (Model 3) Unsustainable
model3 = lm(diet_m ~ aei_closest_std  + treecov_std + disturban_cat_std + distroad_cat_std + popden_std + tlu_std + age_std + education_std + improvedtoilet + improvedwater + sex + timewater_std + wealthindex_std + factor(yeardhs) + factor(country), df_unsust)

```

### check collinearity
```{r}
vif(model1)
vif(model2)
vif(model3)
```


# https://nicholasrjenkins.science/post/data_viz_r/data_visualization_r/
# combining the results from both models into a single data frame
# also adding a new column with the name of each model
```{r}
fit1 <- tidy(model1, conf.int = TRUE) %>% 
  mutate(model = "Overall")

fit2 <- tidy(model2, conf.int = TRUE) %>% 
  mutate(model = "Sustainable")

fit3 <- tidy(model3, conf.int = TRUE) %>% 
  mutate(model = "Unsustainable")

model_results <- bind_rows(fit1, fit2, fit3)

# Filter out rows corresponding to the intercept term, sd__observation and sd__intercept
model_results <- model_results[!(model_results$term %in% c("(Intercept)", "sd__Observation", "sd__(Intercept)")), ]

# keep only the rows that we need, exclude the factor vars coefficients
model_results <- model_results[c(1:13, 48:60, 95:107), ]

label1 = c(
          aeidif_std = "Irrigated area change (Ha)",
          aei_pctdif_std = "Irrigated area percent change",
          aei_pct2000_std = "Irrigated area 2000",
          aeidif_10y_std = "Irrigated area 10y diff",
					aeidif_20y_std = "Irrigated area change 20y",
					aeidif_30y_std = "Irrigated area 30y diff",
					aei_closest_std = "Irrigated area of closest year",
          treecov_std = "Tree cover",
          disturban_std = "Distance from city",
          distroad_std = "Distance from road",
          disturban_cat_std = "Distance from city",
          distroad_cat_std = "Distance from road",
          popden_std = "Population density",
          tlu_std = "Livestock density",
          age_std = "Child age",
          education_std = "Education of household head",
          improvedtoilet = "Improved Sanitation",
          improvedwater = "Improved Water",
          sex = "Male household head",
          timewater_std = "Time to water",
          poorest_std = "Poorest household",
          poorer_std = "Poorer household",
          richer_std = "Richer household",
          richest_std = "Richest household",
          wealthindex_std = "Wealth index",
					yeardhs = "Survey year")

#label2 = c(
#          aeidif_20y_std = "Irrigated area change 20y",
#					aei_closest_std = "Irrigated area of closest year")

label2 = c(aei_closest_std = "Irrigated area of closest year")

# Create a vector of variable names with the desired order
data_labels <- c(
"aei_closest_std","aeidif_10y_std", "aeidif_20y_std", "aeidif_30y_std", "aeidif_std", "aei_pctdif_std", "aei_pct2000_std", "treecov_std", "disturban_std", "distroad_std", "disturban_cat_std", "distroad_cat_std", "popden_std", "tlu_std", "age_std", "education_std", "improvedtoilet",
  "improvedwater", "sex", "timewater_std", "poorest_std", "poorer_std",
  "richer_std", "richest_std", "wealthindex_std", "yeardhs"
)

data_order <- unique(model_results$term)

# Reorder the term variable in your data according to the desired order
model_results$term <- factor(model_results$term, levels = data_labels)

# Create a column for significance labels
model_results$significance <- ifelse(model_results$p.value < 0.05, "*", "")

# Add a column for significance level [USED THIS IN PLOT]
# Jan28,24 I also added the p<0.1 "." as "*" in the column - haven't done it for all prev codes
# so doing one extra * for each coefficient significance to also include the p<0.1 significance, bz the diff in diff regression is marginally significant (Fig2C)
model_results$significance_level <- ifelse(model_results$p.value < 0.001, "****",
                        ifelse(model_results$p.value < 0.01, "***",
                        ifelse(model_results$p.value < 0.05, "**",
                        ifelse(model_results$p.value < 0.1, "*", ""))))

# keep only irrigation coefficients
rows_to_keep <- c(1, 14, 27) # Create a vector of row indices you want to keep
model_results_aei <- model_results[rows_to_keep,] 

# exported it
#write.csv(model_results, "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Combined_results.csv")

# (feb2,25)
# create new variable model1 as Overall, No water stress, Water stress

model_results <- model_results %>%
  mutate(model1 = case_when(
    model == "Sustainable" ~ "No water stress",
    model == "Unsustainable" ~ "Water stress",
    TRUE ~ "Overall"  # Ensure Overall remains unchanged
  )) %>%
  mutate(model1 = factor(model1, levels = c("Overall", "No water stress", "Water stress")))

```


## SUPPLEMENTARY FIGURE S3 (feb2,25 - used this for Manuscript NatSust4)

# Plot for all variables coefficients without aserisks
# Will put asterisks in the ppt as putting them here is not clear enough

```{r}
# Make sure to adjust scale_x_continuous limits such that all points, and error bars are visible
# I used c(-1,0.4) first and bz of that, 2-3 error bars were not visible
ggplot(data = model_results, 
       aes(x = estimate, y = fct_reorder(term, estimate), xmin = conf.low, xmax = conf.high, color = model1)) +
  
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error, group = model),
                 position = position_dodge(width = 0.5),  # Offset the error bars
                 color = "gray", height = 0.2) +
  
  geom_point(shape = 16, position = position_dodge(width = 0.6), size = 2) +
  
  labs(x = "Coefficient Estimate", y = "",
       color = "",  shape = "") +
  scale_x_continuous(limits = c(-0.4, 0.32)) +
  scale_y_discrete(limits = rev(data_order), labels = label1) +
  #scale_color_viridis(discrete = TRUE) +
  #scale_color_brewer(palette = "Dark2") + 
  # https://www.color-hex.com/color-palette/1872
  scale_color_manual(values = c("#0057e7", "#008744", "#ffa700")) +
  ggpubr::theme_pubclean(flip = TRUE)+
  
  # Set font to TW Cen MT - this one doesn't work, but condensed ones do
  theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold", size = 14),
        legend.key = element_blank(),
        axis.text.y = element_text(size = 14), # y axis text size
        axis.text.x = element_text(size = 14), # x axis text size
        legend.text = element_text(size=14) # legend text size
        )
  #theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"))
  
```

### Save the plot
```{r}
save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Figure_S3_no_asterisks.png",

  fig = last_plot(),
  width = 18,
  height = 12,
  dpi = 2400,
  label.color = "black",
  label.size = 1.5,
  axis.textsize = 0.5,
  axis.titlesize = 0.5
  )
```
# ----------------------------------------------------------------------------------------
# PLOT FOR ONLY IRRIGATION VARIABLES [Jan28,24]
# Figure 2- A (Manuscript V9)

# oct26,23 - removed the lines between stars and variable by using geom_text instead of geom_text_repel
# Oct30,23 - unable to make stars go closer to the points, so removed the stars in this fig, and will insert them in ppt
```{r}
# Make sure to adjust scale_x_continuous limits such that all points, and error bars are visible
# I used c(-1,0.4) first and bz of that, 2-3 error bars were not visible
ggplot(data = model_results_aei, 
       aes(x = estimate, y = fct_reorder(term, estimate), xmin = conf.low, xmax = conf.high, color = model)) +
    
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error, group = model),
                 position = position_dodge(width = 0.5),  # Offset the error bars
                 color = "gray", height = 0.1) +
  
  geom_point(shape = 16, position = position_dodge(width = 0.5), size=3) +
  
  # commented the below line for asterisks (oct30,23)
  #geom_text(aes(label = significance_level), nudge_x = -0.02, nudge_y= -0.01, size = 4, show.legend = FALSE ) +  # Add significant labels
  #geom_hline(yintercept = rev(data_order), linetype = "dotted", color = "gray70") +  # Add horizontal lines
  
  labs(x = "Coefficient Estimate", y = "",
       color = "",  shape = "") +
  scale_x_continuous(limits = c(0.03, 0.17)) +
  scale_y_discrete( labels = label2) +
  #scale_color_viridis(discrete = TRUE) +
  #scale_color_brewer(palette = "Dark2") + 
  # https://www.color-hex.com/color-palette/1872
  scale_color_manual(values = c("#0057e7", "#008744", "#ffa700")) +
  ggpubr::theme_pubclean(flip = TRUE)+
  
  # Set font to TW Cen MT - this one doesn't work, but condensed ones do
  theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"),
        legend.key = element_blank(),
        axis.text = element_text(size = 14), # the axis label size
        axis.title = element_text(size = 14), # Adjust the size for axis titles
        legend.text = element_text(size = 14)  # Adjust the size for legend text
        )
  #theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"))
  
```
### Save the plot
```{r}
save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Combined1_aei.png",

  fig = last_plot(),
  width = 18,
  height = 12,
  dpi = 2400,
  label.color = "black",
  label.size = 1.5,
  #axis.textsize = 0.5,
  #axis.titlesize = 0.5
  )
```




## --------------------------------------------------------------------------------------
# Didn't use this
# oct26,23 - removed the lines between stars and variable by using geom_text instead of geom_text_repel
```{r}
# Make sure to adjust scale_x_continuous limits such that all points, and error bars are visible
# I used c(-1,0.4) first and bz of that, 2-3 error bars were not visible

ggplot(data = model_results, 
       aes(x = estimate, y = fct_reorder(term, estimate), xmin = conf.low, xmax = conf.high, color = model)) +
    geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error, group = model),
                 position = position_dodge(width = 0.5),  # Offset the error bars
                 color = "gray", height = 0.2) +
  geom_point(shape = 16, position = position_dodge(width = 0.6)) +
  geom_text(aes(label = significance_level), nudge_x = -0.02, nudge_y= -0.02, size = 3, show.legend = FALSE) +  # Add significant labels
  #geom_hline(yintercept = rev(data_order), linetype = "dotted", color = "gray70") +  # Add horizontal lines
  
  labs(x = "Coefficient Estimate", y = "",
       color = "",  shape = "") +
  scale_x_continuous(limits = c(-0.4, 0.32)) +
  scale_y_discrete(limits = rev(data_order), labels = label1) +
  #scale_color_viridis(discrete = TRUE) +
  #scale_color_brewer(palette = "Dark2") + 
  # https://www.color-hex.com/color-palette/1872
  scale_color_manual(values = c("#0057e7", "#008744", "#ffa700")) +
  ggpubr::theme_pubclean(flip = TRUE)+
  
  # Set font to TW Cen MT - this one doesn't work, but condensed ones do
  theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"),
        legend.key = element_blank())
  #theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"))
  
```


### Save the plot
```{r}
save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Combined1.png",

  fig = last_plot(),
  width = 18,
  height = 12,
  dpi = 2400,
  label.color = "black",
  label.size = 1.5,
  axis.textsize = 0.5,
  axis.titlesize = 0.5
  )
```

# ----------------------------------------------------------------------------------------
# PLOT 
# DIDN'T USE
# Nov22,23 - show significance with other shapes, removed asterisks

```{r}
# Make sure to adjust scale_x_continuous limits such that all points, and error bars are visible
# I used c(-1,0.4) first and bz of that, 2-3 error bars were not visible

ggplot(data = model_results, 
       aes(x = estimate, y = fct_reorder(term, estimate), xmin = conf.low, xmax = conf.high, color = model)) +
  
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error, group = model), position = position_dodge(width = 0.5),  # Offset the error bars
        color = "gray", height = 0.2) +

  geom_point(aes(shape = ifelse(significance %in% c("*", "**", "***"), "filled", "others")), position = position_dodge(width = 0.5), size = 3) +
  scale_shape_manual(values = c("filled" = 17, "others" = 16), guide = "none") +
  scale_size_manual(values = c("filled" = 0.5, "others" = 1)) +
  
  labs(x = "Coefficient Estimate", y = "", color = "", shape = "") +
  
  scale_x_continuous(limits = c(-0.4, 0.32)) +
  scale_y_discrete(limits = rev(data_order), labels = label1) +
  scale_color_manual(values = c("#0057e7", "#008744", "#ffa700")) + # https://www.color-hex.com/color-palette/1872
  
  theme_minimal() +
  theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"),
        legend.key = element_blank(),
        axis.text = element_text(size = 12), # size of axis label size
        axis.title = element_text(size = 12), # size for axis titles
        legend.text = element_text(size = 12),  # size for legend text
        panel.background = element_rect(fill = "white"), # Set background color to white
        legend.position = "top"  # Move the legend to the top
        )  

```
### Save the plot
```{r}
save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Results\\Regression_outputs\\Cluster_level\\Global_v6_closest\\Combined2.png",

  fig = last_plot(),
  width = 18,
  height = 12,
  dpi = 2400,
  label.color = "black",
  label.size = 1.5,
  axis.textsize = 0.5,
  axis.titlesize = 0.5
  )
```

# THIS STD ERROR IS THE SAME AS WE ALREADY HAVE

```{r}
# # Extract the variance-covariance matrix of random effects
# vcov_matrix <- vcov(model1)
# 
# # Extract the correlation matrix from the variance-covariance matrix
# cor_matrix <- cov2cor(vcov_matrix)
# # Extract the standard errors for random effects
# std_errors <- sqrt(diag(vcov_matrix))
# std_errors
# # Assuming your data frame is named 'df'
# fit1_1 <- head(fit1, -3)
# # Create a data frame for the standard errors
# error_data <- data.frame(
#   term = unique(fit1_1$term),  # Assuming your data contains the terms
#   std_error = std_errors)
# # Merge fit1 and error_bars_df
# fit1_2 <- cbind(fit1_1, error_data)
# # THIS STD ERROR IS THE SAME AS WE ALREADY HAVE
```


































