---
title: "Paper2 DHS Diet Diversity - Global Diff in diff regression at division level"
# This code is for diff_data_v4.dta
# children age=>6mo (corresponding with All_data_v6.dta)
# Regressing change in DD on change in AEI at the division level
# D:\Delaware\Work\Paper2_Irrigation_Nutrition\Data\Diff_in_diff_v1

# Fixed effects model

author: "Piyush Mehta"
last updated: Jan26,2025
output: html_document
---

## Running the model for all countries

```{r results='hide', message=FALSE, warning=FALSE}
setwd("D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs")

library(dotwhisker)
library(dplyr)
library('lme4')
library('lmerTest')
library('MuMIn')
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(ggplot2)
library(expss)
library(car)
library(broom.mixed)
library(ggplot2)
library(forcats)
library(extrafont)
library(ggplot2)
library(ggrepel)
#library(tidyverse)
# need to import fonts so that TW Cen font can work
#font_import() # import fonts - only once
loadfonts(device = "win", quiet = TRUE) # load fonts - every session

df = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global.csv')
df_sust = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_sust.csv')
df_unsust = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_unsust.csv')

```

## Label variables for df
# https://cran.r-project.org/web/packages/expss/vignettes/labels-support.html
```{r}
library(expss)
labels <- list(
  aei_diff_std = "Irrigated area change (Ha)",
  treecov_2005_std = "Tree cover",
  disturban_2005_std = "Distance from urban center",
  distroad_2005_std = "Distance from road",
  #disturban_cat_std = "Distance from urban center",
  #distroad_cat_std = "Distance from road",
  popden_2005_std = "Population density",
  tlu_2005_std = "Livestock density",
  age_2005_std = "Child age",
  edu_2005_std = "Education of household head",
  improvedtoilet2005 = "Improved Sanitation",
  improvedwater2005 = "Improved Water",
  sex2005 = "Male household head",
  time_water2005_std = "Time to water",
  wealth2005_std = "Wealth index",
  aei_sust = "Sustainability")

df = apply_labels(df,labels)
df_sust = apply_labels(df_sust,labels)
df_unsust = apply_labels(df_unsust,labels)
```

# (Model 1) Global
# fixed effects

```{r results='hide', message=FALSE, warning=FALSE}

# Before running the model for a country, check which all variables are NA for the country
# Then remove them from the model

# age is age in months
# country is the country name
# v001 is cluster number (cluster_unique)
# educationyearshead in Meredith's data goes from 0 to 21 (v133 variable)
# + poorest_std + richest_std
# Apr26,23 Using the var wealthindex_std and not the 4 binary vars

# Jan14,24 - remember to use the binary vars for sex, improvedtoilet and improvedwater - not the std vars [using their 2005 vars as suggested]

model4 = lm(diet_diff ~ aei_diff_std + age_2005_std + distroad_2005_std + disturban_2005_std +  edu_2005_std +  improvedtoilet2005 + improvedwater2005 +  popden_2005_std + sex2005 + time_water2005_std + tlu_2005_std  + treecov_2005_std + wealth2005_std + factor(country), df)

```


### check collinearity
```{r}
vif(model4)
```


### model coefficients
```{r}
options(width = 200)
summary(model4)
r.squaredGLMM(model4)

#write.csv(summary(model1)$coefficients,"D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_diff_overall.csv")
```

### Plotting estimates
# https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_model_estimates.html
```{r}
plot_model(model4, terms = c("aei_diff_std", "treecov_2005_std", "disturban_2005_std", "distroad_2005_std", "popden_2005_std", "tlu_2005_std", "age_2005_std", "edu_2005_std", "improvedtoilet2005", "improvedwater2005", "sex", "timewater2005_std", "wealth2005_std"), show.values = TRUE, dot.size = 0.5, value.size = 2, value.offset = 0.3, title = "AEI diff overall", xlim = c(-0.5, 0.5))

save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_diff_overall_aei_sust_test.png",
  fig = last_plot(),
  width = 12,
  height = 9,
  dpi = 600,
  label.color = "black",
  label.size = 2.4,
  axis.textsize = 0.75,
  axis.titlesize = 0.5,
  theme(text = element_text(family = "TW Cent"))
  #theme(text = element_text(family = "TW Cent MT Condensed"))
# theme = theme_get(),
  )
```


### marginal and conditional R2
```{r}
r.squaredGLMM(model1)
```

### model anova
```{r}
options(width = 200)
anova(model1)
```

# ----------------------------------------------------------------------------
# (Model 2) Sustainable AEI expansion Global

```{r results='hide', message=FALSE, warning=FALSE}

model_sust1 = lm(diet_diff ~ aei_diff_std + age_2005_std + distroad_2005_std + disturban_2005_std +  edu_2005_std +  improvedtoilet2005 + improvedwater2005 +  popden_2005_std + sex2005 + time_water2005_std + tlu_2005_std  + treecov_2005_std + wealth2005_std + factor(country), df_sust)

```
# model coefficients
```{r}
options(width = 200)
summary(model_sust1)
r.squaredGLMM(model_sust1)
write.csv(summary(model_sust1)$coefficients,"D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_diff_sust.csv")
```

### Plotting estimates
# https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_model_estimates.html
```{r}
plot_model(model_sust1, terms = c("aei_diff_std", "treecov_2005_std", "disturban_2005_std", "distroad_2005_std", "popden_2005_std", "tlu_2005_std", "age_2005_std", "edu_2005_std", "improvedtoilet2005", "improvedwater2005", "sex", "timewater2005_std", "wealth2005_std"), show.values = TRUE, dot.size = 0.5, value.size = 2, value.offset = 0.3, title = "AEI diff sustainable", xlim = c(-0.5, 0.5))

save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_diff_sust.png",
  fig = last_plot(),
  width = 12,
  height = 9,
  dpi = 600,
  label.color = "black",
  label.size = 2.4,
  axis.textsize = 0.75,
  axis.titlesize = 0.5,
  theme(text = element_text(family = "TW Cent"))
# theme = theme_get(),
  )
```

### model anova
```{r}
options(width = 200)
anova(model_sust1)
```



# ----------------------------------------------------------------------------
# (Model 3) Unsustainable AEI expansion Global

```{r results='hide', message=FALSE, warning=FALSE}

model_unsust1 = lm(diet_diff ~ aei_diff_std + age_2005_std + distroad_2005_std + disturban_2005_std +  edu_2005_std +  improvedtoilet2005 + improvedwater2005 +  popden_2005_std + sex2005 + time_water2005_std + tlu_2005_std  + treecov_2005_std + wealth2005_std + factor(country), df_unsust)


```

# model coefficients
```{r}
options(width = 200)
summary(model_unsust1)
r.squaredGLMM(model_unsust1)
write.csv(summary(model_unsust1)$coefficients,"D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_diff_unsust.csv")
```

### Plotting estimates
# https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_model_estimates.html
```{r}
plot_model(model_unsust1, terms = c("aei_diff_std", "treecov_2005_std", "disturban_2005_std", "distroad_2005_std", "popden_2005_std", "tlu_2005_std", "age_2005_std", "edu_2005_std", "improvedtoilet2005", "improvedwater2005", "sex", "timewater2005_std", "wealth2005_std"), show.values = TRUE, dot.size = 0.5, value.size = 2, value.offset = 0.3, title = "AEI diff unsustainable", xlim = c(-0.5, 0.5))

save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_diff_unsust.png",
  fig = last_plot(),
  width = 12,
  height = 9,
  dpi = 600,
  label.color = "black",
  label.size = 2.4,
  axis.textsize = 0.75,
  axis.titlesize = 0.5,
  theme(text = element_text(family = "TW Cent"))
  )
```

### model anova
```{r}
options(width = 200)
anova(model_unsust1)
```

# ----------------------------------------------------------------------------
# PLOT MODELS TOGETHER


```{r results='hide', message=FALSE, warning=FALSE}
library(dotwhisker)
library(dplyr)
library('lme4')
library('lmerTest')
library('MuMIn')
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(ggplot2)
library(expss)
library(car)
library(broom.mixed)
library(ggplot2)
library(forcats)
library(extrafont)
library(ggplot2)
library(ggrepel)
library(viridis)
#library(tidyverse)
# need to import fonts so that TW Cen font can work
#font_import()
#loadfonts(device = "win")

setwd("D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs")

```
# Load all data
```{r}

df = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global.csv')
df_sust = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_sust.csv')
df_unsust = read.csv('D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Global_unsust.csv')

```


# All models
```{r results='hide', message=FALSE, warning=FALSE}

# (Model 1) Overall
model1 = lm(diet_diff ~ aei_diff_std + age_2005_std + distroad_2005_std + disturban_2005_std +  edu_2005_std +  improvedtoilet2005 + improvedwater2005 +  popden_2005_std + sex2005 + time_water2005_std + tlu_2005_std  + treecov_2005_std + wealth2005_std + factor(country), df)

# (Model 2) Sustainable
model2 = lm(diet_diff ~ aei_diff_std + age_2005_std + distroad_2005_std + disturban_2005_std +  edu_2005_std +  improvedtoilet2005 + improvedwater2005 +  popden_2005_std + sex2005 + time_water2005_std + tlu_2005_std  + treecov_2005_std + wealth2005_std + factor(country), df_sust)

# (Model 3) Unsustainable
model3 = lm(diet_diff ~ aei_diff_std + age_2005_std + distroad_2005_std + disturban_2005_std +  edu_2005_std +  improvedtoilet2005 + improvedwater2005 +  popden_2005_std + sex2005 + time_water2005_std + tlu_2005_std  + treecov_2005_std + wealth2005_std + factor(country), df_unsust)

```

### check collinearity
```{r}
vif(model1)
vif(model2)
vif(model3)
```


# https://nicholasrjenkins.science/post/data_viz_r/data_visualization_r/
# combining the results from both models into a single data frame
# also adding a new column with the name of each model
```{r}
fit1 <- tidy(model1, conf.int = TRUE) %>% 
  mutate(model = "Overall")

fit2 <- tidy(model2, conf.int = TRUE) %>% 
  mutate(model = "Sustainable")

fit3 <- tidy(model3, conf.int = TRUE) %>% 
  mutate(model = "Unsustainable")

model_results <- bind_rows(fit1, fit2, fit3)

# Filter out rows corresponding to the intercept term, sd__observation and sd__intercept
model_results <- model_results[!(model_results$term %in% c("(Intercept)", "sd__Observation", "sd__(Intercept)")), ]

label1 <- list(
  aei_diff_std = "Irrigated area change (Ha)",
  treecov_2005_std = "Tree cover",
  disturban_2005_std = "Distance from urban center",
  distroad_2005_std = "Distance from road",
  #disturban_cat_std = "Distance from urban center",
  #distroad_cat_std = "Distance from road",
  popden_2005_std = "Population density",
  tlu_2005_std = "Livestock density",
  age_2005_std = "Child age",
  edu_2005_std = "Education of household head",
  improvedtoilet2005 = "Improved Sanitation",
  improvedwater2005 = "Improved Water",
  sex2005 = "Male household head",
  time_water2005_std = "Time to water",
  wealth2005_std = "Wealth index")

label2 = c(aei_diff_std = "Irrigated area change (Ha)")

# Create a vector of variable names with the desired order
data_labels <- c(
"aei_diff_std","treecov_2005_std", "disturban_2005_std", "distroad_2005_std", "popden_2005_std", "tlu_2005_std", "age_2005_std", "edu_2005_std", "improvedtoilet2005", "improvedwater2005", "sex2005", "time_water2005_std", "wealth2005_std")

# Reorder the term variable in your data according to the desired order
model_results$term <- factor(model_results$term, levels = data_labels)

# Create a column for significance labels
#model_results$significance <- ifelse(model_results$p.value < 0.05, "*", "")

# Add a column for significance level [USED THIS IN PLOT]
# Jan14,24 I also added the p<0.1 "." in the column - haven't done it for all prev codes
model_results$significance_level <- ifelse(model_results$p.value < 0.001, "****",
                        ifelse(model_results$p.value < 0.01, "***",
                        ifelse(model_results$p.value < 0.05, "**",
                        ifelse(model_results$p.value < 0.1, "*", ""))))

# keep only the rows that we need, exclude the factor vars coefficients
rows_to_keep1 <-c(1:13, 25:37, 49:61)
model_results1 <- model_results[rows_to_keep1,]
data_order <- unique(model_results1$term)
#model_results1 <- model_results[c(1:13, 25:37, 49:61), ]

# keep only irrigation coefficients
rows_to_keep <- c(1, 14, 27) # Create a vector of row indices you want to keep
model_results_aei <- model_results1[rows_to_keep, ]

# exported it
#write.csv(model_results1, "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Combined_results.csv")

# create new variable 'model1' as Overall, No water stress, Water stress
model_results1 <- model_results1 %>%
  mutate(model1 = case_when(
    model == "Sustainable" ~ "No water stress",
    model == "Unsustainable" ~ "Water stress",
    TRUE ~ "Overall"  # Ensure Overall remains unchanged
  )) %>%
  mutate(model1 = factor(model1, levels = c("Overall", "No water stress", "Water stress")))

```

# ------------------------------------------------------------------------------
 
# SUPPLEMENTARY FIGURE 5 (Manuscript NatSust4 - Feb2,25)  [USED THIS]

# Plot for all coefficient variables 
# oct26,23 - removed the lines between stars and variable by using geom_text instead of geom_text_repel

```{r}
# Make sure to adjust scale_x_continuous limits such that all points, and error bars are visible

ggplot(data = model_results1, 
       aes(x = estimate, y = fct_reorder(term, estimate), xmin = conf.low, xmax = conf.high, color = model1)) +
  
  # Error bars
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error, group = model),
                 position = position_dodge(width = 0.5),  # Offset the error bars
                 color = "gray", height = 0.2) +
  
  geom_point(shape = 16, position = position_dodge(width = 0.6), size=2) +

  labs(x = "Coefficient Estimate", y = "",
       color = "",  shape = "") +
  scale_x_continuous(limits = c(-4.2, 2.84)) +
  #scale_y_discrete(labels = label1) +
  scale_y_discrete(limits = rev(data_order), labels = label1) +

  # https://www.color-hex.com/color-palette/1872
  scale_color_manual(values = c("#0057e7", "#008744", "#ffa700")) +
  ggpubr::theme_pubclean(flip = TRUE)+
  
  # Set font to TW Cen MT - this one doesn't work, but condensed ones do
  theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"),
        legend.key = element_blank(),
        axis.text = element_text(size = 12), # the axis label size
        axis.title = element_text(size = 12), # Adjust the size for axis titles
        legend.text = element_text(size = 12)  # Adjust the size for legend text
        )
  
```

### Save the plot
```{r}
save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Figure_S5_without_asterisks.png",
 
   fig = last_plot(),
   width = 18,
   height = 12,
   dpi = 2400,
   label.color = "black",
   label.size = 1.5,
#   axis.textsize = 0.5,
#   axis.titlesize = 0.5
   )
```

# ------------------------------------------------------------------------------ 
# FIGURE 2C (Manuscript NatSust2 Jan1,25) [USED THIS]

# Plot for only AEI coefficient variable 

```{r}
# Make sure to adjust scale_x_continuous limits such that all points, and error bars are visible

ggplot(data = model_results_aei, 
       aes(x = estimate, y = fct_reorder(term, estimate), xmin = conf.low, xmax = conf.high, color = model)) +
  
  # Error bars
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error, group = model),
                 position = position_dodge(width = 0.5),  # Offset the error bars
                 color = "gray", height = 0.1) +
  
  geom_point(shape = 16, position = position_dodge(width = 0.5), size=3) +

  labs(x = "Coefficient Estimate", y = "",
       color = "",  shape = "") +
  scale_x_continuous(limits = c(-1.15, 0.26)) +
  scale_y_discrete(labels = label2) +

  # https://www.color-hex.com/color-palette/1872
  scale_color_manual(values = c("#0057e7", "#008744", "#ffa700")) +
  ggpubr::theme_pubclean(flip = TRUE)+
  
  # Set font to TW Cen MT - this one doesn't work, but condensed ones do
  theme(text = element_text(family = "Tw Cen MT Condensed Extra Bold"),
        legend.key = element_blank(),
        axis.text = element_text(size = 14), # the axis label size
        axis.title = element_text(size = 14), # Adjust the size for axis titles
        legend.text = element_text(size = 14)  # Adjust the size for legend text
        )
  
```

### Save the plot
```{r}
save_plot(
  "D:\\Delaware\\Work\\Paper2_Irrigation_Nutrition\\Data\\Diff_in_diff_v1\\regression_outputs\\Figure_2C_without_asterisks.png",
 
   fig = last_plot(),
   width = 18,
   height = 12,
   dpi = 2400,
   label.color = "black",
   label.size = 1.5,
#   axis.textsize = 0.5,
#   axis.titlesize = 0.5
   )
```
# ------------------------------------------------------------------------------ 


